Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2020-04-23 manuscript/manuscript.tex
updated ms

>>>>

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/fig-both-trunc.pdf}

  \caption{$G(t)$ trajectories (left) and temporal covariances (right) from
    truncation selection simulations for different numbers of individuals
    selected (line color). The dashed lines indicate the $G(t)$ trajectories
    calculated \emph{including} fixed sites, while the solid lines exclude
    fixed sites.

    both
  including fixed sites (solid lines) and not including fixed sites (dashed
lines). The dashed lines are identical to those in Supplementary Materials
Figure \ref{suppfig:supp-bgs-g}. As expected, including fixed sites shrinks the
$G(t)$ towards zero, and in some cases, they can become negative.}
